msAggr_seurat

### 2021-09-16 msAggr/msAggr_seurat.Rmd
completing code for pseudobulk analysis

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
# library(clustree)
```
store session info
```{r}
sink("msAggr_seurat-v1.20210623")
sessionInfo()
sink()
```

@@

>>>>

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
# library(clustree)
```

@@

## Store session info
```{r}
sessionInfo.filename <- paste0(projectName, "_sessionInfo.txt")
sink(sessionInfo.filename)
sessionInfo()
sink()
```
